%% 摘要页
\newpage
\section*{\markboth{摘要}{摘要}{摘\quad 要}}
\pagenumbering{Roman} %
\medskip
随机变量的独立性非参数假设检验一直以来就是统计学上比较关注的问题。Jing 和 Zhu(1996) 提出了基于pp法和bootstrap法的一种B-K-R型检验统计量。Norbert Henze 和 Ya.Yu.Nikitin(2003)引入了积分经验过程。Jing和Wang（2006）利用积分经验过程检验多元分布函数的相等性。本文在这些文章的基础上，提出了高维情况下基于投影积分经验过程的 Kolmogorov-Smirnov 和 Cramer-VonMises(C-V) 检验统计量检验随机变量的独立性。
Bootstrap 统计量用于逼近所提出的统计量的临界值,并证明了在原假设成立时他们有相同的经验分布。
数论的方法用于有效的计算bootstrap临界值。最后本文给出了大量的数值模拟。
\medskip
\par
{\heiti 关键词 ：}Bootstrap统计量，积分经验分布函数，积分经验过程

\par
\vspace{1cm}
\noindent\begin{tabular}{l}
\hline\hline
\hspace*{14.5cm}
\end{tabular}

\begin{center}
{\bf \Large Abstract}\\
\vskip 0.6cm
\end{center}
\par
Testing the joint independence of variables has long been an
interesting issue in statistical inference.Jing and Zhu(1996)
proposed  B-K-R type tests based on the projection pursuit technique
and bootstrap method.Henze and Ya.Yu.Nikitin(2003) introduced the
integrated empirical processes.Jing and Wang(2006) used the
integrated empirical processes to test the equality of multivariate
distributions.Based on the above ,in this paper we will introduce
the projected integrated empirical processes of Cramer-VonMises
statistics and Kolmogorov-Smirnov statistics for testing the joint
independence of variables in high dimension space.The bootstrap is
used for determining the approximate critical values. An
approximation is derived by Number-theoretic method for the
bootstrap statistics suggested. Several simulation experiments are
performed.
\medskip
\par

{\bf Key words：}Bootstrap，Kolmogorov-Smirnov statistics

%%% 空一页
\newpage 
\mbox{} 